The Evolution of Phenotypically Invariant Genetic Networks

### 2021-08-11 kalman_walk_paper.tex
minor adjustment

Although the phrase ``system drift'' as we use it implies neutral changes,
it does not mean that these changes are induced purely by neutral genetic drift.
Selection could dramatically accelerate speciation by the same process --
i.e., \emph{genetic draft} \citep{gillespie2000genetic}.
For instance, \citet{mani1990mutational} showed that populations
developed incompatibilities as they independently evolved towards the same quantitative trait optimum,
as different alleles fix in different populations. \llabel{citemani}
Fluctuating selection has similarly been shown to accelerate speciation
in some models \citep{bell2010fluctuating,barton2001role}.
Under our model, populations evolving towards different optimal phenotypes will always produce less fit hybrids,
as the hybrid phenotypes will be displaced from both parental optimums -- that is maladapted to both parental environments.
This suggests that fluctuating selection -- if not synchronized between populations -- should diminish hybrid fitnesses.
In the case where fluctuations are synchronized, due to the size of the neutral system space, 
populations may arrive at different system organizations when returning to previous phenotypes at a rate faster than by drift alone. \revpoint{1}{3}

>>>>

Although the phrase ``system drift'' as we use it implies neutral changes,
it does not mean that these changes are induced purely by neutral genetic drift.
Selection could dramatically accelerate speciation by the same process --
e.g., by genetic draft \citep{gillespie2000genetic} or pleiotropic selection.
For instance, \citet{mani1990mutational} showed that populations
developed incompatibilities as they independently evolved towards the same quantitative trait optimum,
as different alleles fix in different populations. \llabel{citemani}
Fluctuating selection has similarly been shown to accelerate speciation
in some models \citep{bell2010fluctuating,barton2001role}.
Under our model, populations evolving towards different optimal phenotypes will always produce less fit hybrids,
as the hybrid phenotypes will be displaced from both parental optima,
and so maladapted to both parental environments.
This suggests that fluctuating selection -- if not synchronized between populations -- should diminish hybrid fitnesses.
In the case where fluctuations are synchronized, due to the size of the neutral system space, 
populations may arrive at different system organizations when returning to previous phenotypes at a rate faster than by drift alone. \revpoint{1}{3}
